\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
fix error
Request from AQ

@@

Considering the short delay for a communication between
neurons, slow events can be neglected to retrieve direct relationships.
Indeed, for a direct relationship, i.e. a neuron firing directly implying another
neuron to fire, the average time is about $1ms$ or $2ms$ while the
fluorescent signal time resolution is $20ms$. In order to find out which neurons
are directly related, it is only necessary to look after the burst signal, or
in other words, whether the signal varies. In our approach, we choose to apply
an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x_{t-1}^i$.

@@

For the directory method, only filters defined by Equations
\ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
used.

>>>>

\textcolor{red}{It may be useful to rewritte the following lines but I add it to not forget about a plan (request from AQ)}
In section \ref{sec:filter}, we will describe how we filter the fluorescent calcium imaging signal.
In section \ref{sec:inference}, we will characterize our algorithm from a theoretical point of view. 
In section \ref{sec:results}, we will present some results and give a critical comparision with other inference methods.
In appendix \ref{app:optimized}, we describe a fully tuned version of our algorithm which has won the Connectomics challenge.

@@

Considering the short delay for a communication between
neurons, slow events can be neglected to retrieve direct relationships.
Indeed, for a direct relationship, i.e. a neuron firing directly implying another
neuron to fire, the average time is about $1ms$ or $2ms$ while the
fluorescent signal time resolution is $20ms$. In order to find out which neurons
are directly related, it is only necessary to look after the burst signal, or
in other words, whether the signal varies. In our approach, we choose to apply
an asymmetrical discrete derivative : $x^{t,d}_{i} \leftarrow x^{t}_i - x^{t-1}_i$.

@@

% For the directory method, only filters defined by Equations
% \ref{eq:low-pass}, \ref{eq:high-pass} and \ref{eq:hard-treshold-filter} were
% used.
